This is a title

### 2024-05-29 paper/sections/04-method.tex
made preprocessing diagram
Add vision transformer section

\subsubsection{XGBoost}
XGBoost is an open source gradient tree boosting package~\cite{xgboost}. 
For this research we used the xgbregression model It has shown broad success accross a range of tasks, performing on par with or better than most equivalent and Automated Machine learning approaches~\cite{xgbcomp}.
\subsubsection{ResNet}
ResNet (Residual Network) is an architecture for deep neural networks that speeds up the training process through the use of residual connections~\cite{resnet}. 
For the purposes of this research we focused on ResNet18, the 18 layer deep variation with some modifications to accomodate the shape of the input data and the required output. 
\subsubsection{[Transformer]}

@@

\newcommand{\nspecies}{N_{\text{species}}}

@@

\subsubsection{Species scoring}
\begin{figure}
    \begin{center}
        \input{figs/model-diagram.tex}
        \caption{The structure of the scoring ensemble from data through to individual species score outputs.}
    \end{center}\label{fig:score-structure}
\end{figure}
\subsubsection{Species counts}
\begin{figure}
    \begin{center}
        \input{figs/count-diagram.tex}
        \caption{The counts ensemble through to final outputs.}
    \end{center}\label{fig:count-structure}
\end{figure}
\subsection{Metrics}

>>>>

\subsubsection{XGBoost}
XGBoost is an open source gradient tree boosting package~\cite{xgboost}.
For this research we used the xgbregression model It has shown broad success accross a range of tasks, performing on par with or better than most equivalent and Automated Machine learning approaches~\cite{xgbcomp}.
\subsubsection{ResNet}
ResNet (Residual Network) is an architecture for deep neural networks that speeds up the training process through the use of residual connections~\cite{resnet}.
For the purposes of this research we focused on ResNet18, the 18 layer deep variation with some modifications to accomodate the shape of the input data and the required output.
\subsubsection{Transformer}
Vision transformers (ViTs) have emerged as a novel approach to image classification, often outperforming traditional convolutional neural networks (CNNs) by leveraging self-attention mechanisms originally developed for machine translation \cite{vaswani2017attention}. Transformer now underpin some of the most powerful Large Language models \cite{brown2020language}. By tokenizing images into fixed-size patches and encoding them into embeddings for transformer layers to process, ViTs excel at capturing long-range dependencies within an image, enabling a more holistic interpretation of visual context compared to CNN's local focus \cite{dosovitskiy2021image}. This methodological shift allows the models to effectively decipher complex scenes and interactions that are typically challenging for traditional architectures.

Often ViT-based models are often developed for large high resolution imagery. This was not the case for this application where the satellite images were a modest 128x128 pixels. We believed that the ability of transformer based models to capture to intricate regional relationships. Would be beneficial to the task of species classification.

@@

\subsubsection{Preprocessing}

\begin{figure}\label{fig:preproc}
    \begin{center}
        \input{figs/pca-diagram.tex}
        \caption{Preprocessing the data for use in the count prediction and XGBoost pseudo-probability models}
    \end{center}
\end{figure}

\subsubsection{Main Process}
\newcommand{\nspecies}{N_{\text{species}}}

@@

% \subsubsection{Species scoring}
% \begin{figure}
%     \begin{center}
%         \input{figs/model-diagram.tex}
%         \caption{The structure of the scoring ensemble from data through to individual species score outputs.}
%     \end{center}\label{fig:score-structure}
% \end{figure}
% \subsubsection{Species counts}
% \begin{figure}
%     \begin{center}
%         \input{figs/count-diagram.tex}
%         \caption{The counts ensemble through to final outputs.}
%     \end{center}\label{fig:count-structure}
% \end{figure}
% \subsection{Metrics}
